method

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added root directory

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(targets)
library(readxl)
library(here)
```

@@

stim

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(targets)
library(readxl)
library(here)

# set top level directory to source file
here::i_am("flag_project_root.txt")
```

@@

StimNeg
